A new look at Pompeiu Triangles

### 2023-10-18 mathPaper/pompeiuTriangles.tex
generalized

>>>>

Note that Eq. (\ref{eq:psum4}) is valid for any triangle $ABC$ and any point $P$ in the interior of the triangle. If triangle $ABC$ is not equilateral, one can use formula $\cos(2x)=1-2\sin(x)^2$ along with the law of sines to derive a more general formula for the distance of $P$ to the circumcircle of $ABC$, i.e.

\begin{equation}
OP^2=R^2-\frac{k_1k_2c^2+k_1k_3b^2+k_2k_3a^2}{(k_1+k_2+k_3)^2}
\label{eq:psum6}
\end{equation}
where $a$, $b$ and $c$ are the sides of triangle $ABC$.
Combined with the formula for the area of a generalized Pompeiu triangle (Benyi and Casu 2009), this formula can be used to show that the locus of a point associated with a generalized Pompeiu triangle with constant area is still a circle with the same center as the circumcircle of $\Delta ABC$. The derivation of the formula for the area of a generalized Pompeiu triangle using the approach described in the previous sections for a regular Pompeiu triangle is straightforward and requires the extension of Eqs. (\ref{eq:area2}) and (\ref{eq:centroid2}) to their general forms.
